Meta analysis of reprocessed RNASeq data from AMP-AD for hg38 Reprocessed Data (all 7 brain regions)

### 2021-11-17 code/RNA-Seq_Meta_Analysis.Rmd
New version RNA-Seq Weights

```{r get.exp}
# Function to read tsv/csv files from synapse
downloadFile <- function(id, tissue){ 
  dat <- fread(synapser::synGet(id)$path, data.table = F)
  dat$tissue <- tissue
  return(data)
}
# Read covariates
covar.ids = c(ROSMAP_DLPFC = 'syn26340637 ', 
              ROSMAP_PCC = 'syn26350606',
              ROSMAP_ACC = 'syn26374583 ',
              MSSM_FP = 'syn26453689', 
              MSSM_IFG = 'syn26454154', 
              MSSM_PHG = 'syn26453943', 
              MSSM_STG = 'syn26454639', 
              MAYO_TCX = 'syn26374583')
#_tissue

@@

all.used.ids = c(all.used.ids, as.character(expr.ids))
downloadFile <- function(id, tissue){ 
  fread(synapser::synGet(id)$path, data.table = F)
}
expr =  expr.ids %>%
  lapply(downloadFile) %>%
  plyr::join_all(type = 'full')
```

>>>>

```{r get.exp}
# Function to read tsv/csv files from synapse
downloadFile <- function(id){ 
  fread(synapser::synGet(id)$path, data.table = F)
}
# Read covariates
covar.ids = c(ROSMAP_DLPFC = 'syn26340637 ', 
              ROSMAP_PCC = 'syn26350606',
              ROSMAP_ACC = 'syn26374583 ',
              MSSM_FP = 'syn26453689', 
              MSSM_IFG = 'syn26454154', 
              MSSM_PHG = 'syn26453943', 
              MSSM_STG = 'syn26454639', 
              MAYO_TCX = 'syn26374583')
#_tissue

@@

all.used.ids = c(all.used.ids, as.character(expr.ids))

expr =  expr.ids %>%
  lapply(downloadFile) %>%
  plyr::join_all(type = 'full')
```
